%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Patrick James Byrne} % Your name
\address{244 Hudson St. \\ Cornwall-on-Hudson, NY 12520} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(570)~$\cdot$~702~$\cdot$~1270 \\ pjb2132@columbia.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Columbia University } \hfill {\em New York, NY, 2009-Present} \\ 
Ph.D. Candidate in Plasma Physics \hfill {\em  Expected Graduation: August 2016}\\
M.S., M.Phil. in Plasma Physics\smallskip 

{\bf Carnegie Mellon University } \hfill {\em Pittsburgh, PA, 2002-2006} \\ 
B.S. in Physics \\
Minor in Engineering Studies \smallskip

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{United States Military Academy}{Jun 2015 - Present}{Physics Instructor}{West Point, NY}
\item	Teach four sections of calculus-based introductory physics in a classroom and laboratory setting.
\item 	Study student outcomes in a university-wide analysis project prompted by curriculum changes.
\item	Maintain and track lab equipment used for classroom demonstrations and lab instruction.
\item   Maintain a gradebook and return timely feedback to cadets on all graded events, including instructor-designed homeworks and quizzes.
\item 	Provide one-on-one and group office hours for additional instruction.  Provide counsel to failing cadets on time-management, study habits, goal-setting and success strategies.

\end{rSubsection}


\begin{rSubsection}{Columbia University Plasma Lab}{Aug 2009 - Present}{Graduate Research Student}{New York, NY}
\item	Thesis topic: Effects of Magnetic Shaping on MHD modes in Tokamaks.
\item	Designed, installed, and maintained a low-impedance/high-voltage, plasma-shaping electromagnet, including 2MW quick-start capacitive pulsed power supply and current monitor.
\item	Analyzed large and highly variable datasets to determine effects of shaping on plasma stability.
\item   Maintained, upgraded, and/or created all necessary diagnostics and simulation/analytic software.

\end{rSubsection}

\begin{rSubsection}{Lutron Electronics}{June 2006 - Sept 2007}{Project Physicist - Existing Product Support}{Coopersburg, PA}
\item	Reengineered Lutron's flagship products to meet and exceed environmental, cost, QA, supply chain, and production line constraints.
\item	Oversaw day-to-day operation of Lutron’s color compliance program.

\begin{rSubsubsection}
\item Mediated Lutron's disputes with suppliers and customers.
\item Characterized different spectrophotometers for accuracy, precision and consistency.
\item Drew up operation procedures and best practices for color measurement and quality control.
\item Provided training to QA managers and project engineers.
\end{rSubsubsection}

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Proficiencies}

Mill/Lathe Machining, ProE, Python, C, Matlab, SPICE, R, IDL, HTML, Microsoft Office

\end{rSection}

%----------------------------------------------------------------------------------------
%	Interests
%----------------------------------------------------------------------------------------

\begin{rSection}{Interests}

\begin{tabular}{ @{} >{}l @{\hspace{6ex}} l }
Homebrewing, Distance running, DIY Electronics
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------

\end{document}
